### 2022-09-28 main/chapter_context.tex
add some susy text

Another example is the hierarchy problem of the Higgs boson mass $m(h)$,
which notes that the energy scale of new heavy particles add quadratically to
$m(h)^2$ through direct or indirect couplings.
With any particles near the Planck scale $\sim 10^{18}\,\eV[G]$, implementing
the observed $m(h) \sim 10^{2}\,\eV[G]$ therefore requires finely-tuned
cancellations between positive and negative additions.
New fermions subtract from $m(h)$ and new scalars add by similar amounts,
so new models can implement this fine-tuning by inserting only matched pairs of
fermions and scalars --- this is the strategy of supersymmetric models.

\subsection{Supersymmetric models}
\label{sec:context_susy}

% supersymmetry

% supersymmetric models

% fermion boson multiplets

>>>>

Another example is the `hierarchy' problem of the Higgs boson mass $m(h)$,
which notes that new particles at a heavy mass scale $\Lambda$ induce changes
of $\Delta m(h)^2 = \mathcal{O}(\Lambda^2)$,
through direct or indirect couplings.
With any particles near the Planck scale $\Lambda \sim 10^{18}\,\eV[G]$,
implementing the observed $m(h) \sim 10^{2}\,\eV[G]$ therefore requires
finely-tuned cancellations between positive and negative contributions.
New fermions subtract from $m(h)$ and new scalars add by similar amounts,
so new models can implement this fine-tuning by inserting only matched sets of
fermions and bosons.
This solution is the strategy of supersymmetric models.

\subsection{Supersymmetric models}
\label{sec:context_susy}
Supersymmetry is the concept of symmetry under the operation of exchanging
bosonic and fermionic states, and supersymmetric models use supersymmetry in
their construction.
Supersymmetry itself is not a model, but if our searches did hypothetically
find evidence for any supersymmetric model, then that would be evidence for
supersymmetry in nature.

Nature is not totally supersymmetric.
If it were, then there would be bosonic `superpartners' for each of the known
fermions (and vice versa) with the same masses and charges, and those
`sparticles' would have been seen long ago.
However, like the broken symmetry of the Standard Model gauge group,
supersymmetry could still participate in a broken condition.

Any new model must include the observational facts of the Standard Model,
and with supersymmetry the minimum viable product is the
Minimal Supersymmetric Standard Model (MSSM).
% fermion boson multiplets
